Learning From Massive Noisy Labeled Data for Image Classification

### 2015-04-10 ext.tex
Polish the extended abstract

\noindent
Deep learning with large-scale supervised training data has shown very impressive improvement on image classification challenge~\cite{krizhevsky2012imagenet}. However, it requires reliable annotations from millions of images which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems. Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.

@@

Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels. Semi-supervised learning methods~\cite{lee2013pseudo} can also be employed by simply discarding all the noisy labels. Researchers have also studied the transferability of Convolutional Neural Networks (CNNs) by finetuning an ImageNet pretrained model on smaller datasets of specific tasks~\cite{oquab2014learning}. However, these methods cannot fully utilize the massive noisy labeled data, which may lead to suboptimal results.

@@

Our proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables. We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the training process of CNNs. Experiments on the collected dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.

>>>>

\noindent
Deep learning from large-scale supervised training dataset has shown very impressive improvement on image classification challenge~\cite{krizhevsky2012imagenet}. However, it requires reliable annotations from millions of images which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems. Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.

@@

Although annotating all the data is costly, it is often easy to obtain a small amount of clean labels. Semi-supervised learning methods~\cite{lee2013pseudo} can be employed by simply discarding all the noisy labels. Researchers have also studied the transferability of Convolutional Neural Networks (CNNs) by finetuning an ImageNet pretrained model on smaller datasets of specific tasks~\cite{oquab2014learning}. However, these methods cannot fully utilize the massive noisy labeled data, which may lead to suboptimal results.

@@

Our proposed probabilistic model builds the relations among images, noisy labels, ground truth labels, and noise types, where the latter two are treated as latent variables. We use the Expectation-Maximization (EM) algorithm to solve the problem and integrate it into the deep learning framework. Experiments on the collected dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
